---
title: "Appendix"
format: html
execute:
  echo: false
  message: false
  warning: false
---

```{r}
#| message: false
#| warning: false
library(tidyverse)
library(tidymodels)
library(broom)
library(gt)
library(marginaleffects)
```

```{r}
#| cache: true
#| message: false
#| warning: false
x <- read_csv("digital_marketing_campaign_dataset - digital_marketing_campaign_dataset.csv.csv", show_col_types = FALSE) |> 
  select(Conversion, CampaignChannel, Age, Gender, Income, AdSpend, WebsiteVisits, PagesPerVisit, TimeOnSite, SocialShares, PreviousPurchases) |> 
  mutate(
    Conversion = factor(Conversion, levels = c(0, 1)),
    CampaignChannel = factor(CampaignChannel),
    Gender = factor(Gender)
  )
```

```{r}
#| cache: true
fit_campaign <- logistic_reg(engine = "glm") |> 
  fit(
    Conversion ~ CampaignChannel + Age + Gender + Income + AdSpend + WebsiteVisits + PagesPerVisit + TimeOnSite + SocialShares + PreviousPurchases, 
    data = x |> mutate(Income = Income / 10000, AdSpend = AdSpend / 100)
  )
```

## Full Model Tibble
```{r}
logistic_reg(engine = "glm") |> 
  fit(
    Conversion ~ CampaignChannel + Age + Gender + Income + AdSpend + WebsiteVisits + PagesPerVisit + TimeOnSite + SocialShares + PreviousPurchases, 
    data = x |> mutate(Income = Income / 10000, AdSpend = AdSpend / 100)
  ) |> 
  tidy(conf.int = TRUE) |> 
  gt() |> 
  fmt_number(decimals = 5) |> 
  tab_header(
    title = "Logistic Regression Model: Conversion with Campaign Channel and other Covariates",
    subtitle = "Adjusting for other covariates"
  ) |> 
  tab_source_note(source_note = "Source: Digital Marketing Campaign Dataset")
```

* **Age:** Although positive, the confidence interval for age passes zero, so age does not have a clear effect on the probability of purchasing the product.

* **Gender:** Males have a slightly higher chance for conversion. However, the confidence interval for gender passes zero, so gender does not have a clear effect on the probability of purchasing the product.

* **Income:** The confidence interval for income passes zero, so income does not have a clear effect on the probability of purchasing the product.

* **AdSpend:** The confidence interval for ad spend does *not* pass zero, so higher ad spend increases the probability of purchasing the product.

* **WebsiteVisits:** The confidence interval for website visits does *not* pass zero, so visiting the website more often increases the probability of purchasing the product.

* **PagesPerVisit:** The confidence interval for pages per visit does *not* pass zero, so viewing more pages per visit increases the probability of purchasing the product.

* **TimeOnSite:** The confidence interval for time on site does *not* pass zero, so spending more time on site increases the probability of purchasing the product.

* **SocialShares:** The confidence interval for social shares passes zero, so social sharing does not have a clear effect on the probability of purchasing the product.

* **PreviousPurchases:** The confidence interval for previous purchases does *not* pass zero, so having more previous purchases increases the probability of purchasing the product

**Overall:** Demographic variables like age, gender, and income do not have significant effects of conversion, but rather demostrations of personal interest like time on site do.

## More Comparisons
```{r}
avg_comparisons(extract_fit_engine(fit_campaign)) |> 
  select(-statistic, -p.value, -s.value) |> 
  gt() |> 
  fmt_number(decimals = 5) |> 
  tab_header(
    title = "Average Comparisons (Marginal Effects)",
    subtitle = "Estimating average causal effects of campaign channels and covariates"
  ) |> 
  tab_source_note(source_note = "Source: Digital Marketing Campaign Dataset")
```
