---
title: "Overview"
author: "Henry Yang"
format: html
execute:
  echo: false
  message: false
  warning: false
---

```{r}
#| message: false
#| warning: false
library(tidyverse)
library(tidymodels)
library(broom)
library(gt)
library(marginaleffects)
```

```{r}
#| message: false
#| warning: false
read_csv("digital_marketing_campaign_dataset - digital_marketing_campaign_dataset.csv.csv", show_col_types = FALSE) |> 
  drop_na() |> 
  group_by(CampaignChannel) |> 
  summarize(mean_conversion = mean(Conversion)) |> 
  ggplot(aes(x = CampaignChannel, y = mean_conversion, fill = CampaignChannel)) +
  geom_col(show.legend = FALSE) +
  scale_y_continuous(labels = scales::percent) +
  coord_cartesian(ylim = c(0.75, NA)) +
  theme_minimal() +
  labs(
    title = "Average Conversion Rate by Campaign Channel",
    subtitle = "PPC and Referrals have the highest conversion rates, while Social Media has the lowest.",
    x = "Campaign Channel",
    y = "Average Conversion Rate",
    caption = "Source: Digital Marketing Campaign Dataset"
  )
```

## Summary
The medium in which a campaign is delivered can significantly impact its effectiveness. This model uses data from the Digital Marketing Campaign dataset by Zafar to try to answer the question: What is the average causal effect of getting an email, compared to seeing a social media post, on the probability that a customer purchases a product? One significant potential weakness of this model is how we don't know if treatment assignment was random. If treatment assignment wasn't random, the estimates will likely be biased and would need greater 95% confidence intervals than those predicted. This model models Conversion as a Bernoulli variable which is a logistic function of CampaignChannel, Age, Gender, Income, AdSpend, WebsiteVisits, PagesPerVisit, TimeOnSite, SocialShares, and PreviousPurchases. One quantity of interest is, adjusting for all the covariates, the average causal effect of Social Media as a means of campaigning, compared to receiving an Email as a means of campaigning, on the probability that a customer purchases a product is -0.000174, with a confidence interval between -0.023284 to 0.022936. In other words, compared to Emails, receiving a Social Media treatment resulted in a 0.0174 percentage point increase in the probability that you'll buy a product (confidence interval: -2.3284 to 2.2936 percentage points). This estimate might be wrong because of the vagueness between some campaign channels as they can overlap, and conversion rates also seem to have had a distribution shift due to having much more data on customers who actually purchased to product. Additionally, the effects of advertisements may have changed between the time the data was collected (~2024) and the present day. So, the confidence intervals should be widened for more accuracy, although the causal effect isn't much to begin with.
