---
title: "Overview"
author: "Henry Yang"
format: html
execute:
  echo: false
  message: false
  warning: false
---

```{r}
#| message: false
#| warning: false
library(tidyverse)
library(tidymodels)
library(broom)
library(gt)
library(marginaleffects)
```

```{r}
#| cache: true
#| message: false
#| warning: false
x <- read_csv("digital_marketing_campaign_dataset - digital_marketing_campaign_dataset.csv.csv", show_col_types = FALSE) |> 
  select(Conversion, CampaignChannel, Age, Gender, Income, AdSpend, WebsiteVisits, PagesPerVisit, TimeOnSite, SocialShares, PreviousPurchases) |> 
  mutate(
    Conversion = factor(Conversion, levels = c(0, 1)),
    CampaignChannel = factor(CampaignChannel),
    Gender = factor(Gender)
  )
```

```{r}
#| cache: true
fit_campaign <- logistic_reg(engine = "glm") |> 
  fit(
    Conversion ~ CampaignChannel + Age + Gender + Income + AdSpend + WebsiteVisits + PagesPerVisit + TimeOnSite + SocialShares + PreviousPurchases, 
    data = x |> mutate(Income = Income / 10000, AdSpend = AdSpend / 100)
  )
```

```{r}
#| message: false
#| warning: false
read_csv("digital_marketing_campaign_dataset - digital_marketing_campaign_dataset.csv.csv", show_col_types = FALSE) |> 
  drop_na() |> 
  group_by(CampaignChannel) |> 
  summarize(mean_conversion = mean(Conversion)) |> 
  ggplot(aes(x = CampaignChannel, y = mean_conversion, fill = CampaignChannel)) +
  geom_col(show.legend = FALSE) +
  scale_y_continuous(labels = scales::percent) +
  coord_cartesian(ylim = c(0.75, NA)) +
  theme_minimal() +
  labs(
    title = "Average Conversion Rate by Campaign Channel",
    subtitle = "PPC and Referrals have the highest conversion rates, while Social Media has the lowest.",
    x = "Campaign Channel",
    y = "Average Conversion Rate",
    caption = "Source: Digital Marketing Campaign Dataset"
  )
```

### Interpretation
Overall conversion rates for all campaign channels. Email and Social Media seem to have the same conversion rate. SEO (Search Engine Optimization) has a slightly higher conversion rate, and PPC (Pay-Per-Click) and Referrals have the highest and almost the same conversion rates.

```{r}
plot_predictions(
  extract_fit_engine(fit_campaign), 
  condition = c("Income", "CampaignChannel"), 
  draw = FALSE
) |> 
  ggplot(aes(x = Income, y = estimate, color = CampaignChannel, fill = CampaignChannel)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, color = NA) +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Predicted Probability of Purchasing by Campaign Channel and Income",
    subtitle = "Income levels also have only subtle impacts on conversion probability.",
    x = "Income ($10,000s)",
    y = "Conversion Percentage",
    caption = "Source: Digital Marketing Campaign Dataset",
    color = "Campaign Channel",
    fill = "Campaign Channel"
  )
```

### Interpretation
Including income as a covariate, this model reinforces the claim of Social Media and Email having similar conversion rates. The two lines are directly on top of each other, almost indiscernible. Besides that, income only has a subtle effect on conversion.

**Key note:** Realistic conversion rates are likely much lower in percent, but should share the same slope (Distribution shift). So, this shouldn't affect the causal effect between campaign channels.

## Summary
### Data and Question
The medium in which a campaign is delivered can significantly impact its effectiveness. This model uses data from the Digital Marketing Campaign dataset by Zafar to try to answer the question: What is the average causal effect of getting an email, compared to seeing a social media post, on the probability that a customer purchases a product? 

### Concerns
One significant potential weakness of this model is how we don't know if treatment assignment was random. If treatment assignment wasn't random, the estimates will likely be biased and would need greater 95% confidence intervals than those predicted. 

### Model
This model models Conversion as a Bernoulli variable which is a logistic function of CampaignChannel, Age, Gender, Income, AdSpend, WebsiteVisits, PagesPerVisit, TimeOnSite, SocialShares, and PreviousPurchases. 

### Conclusions
Adjusting for covariates, the average causal effect of Social Media as a means of campaigning, compared to receiving an Email, on the probability that a customer purchases a product is -0.000174, with a confidence interval between -0.023284 to 0.022936. However, *since we don't know if treatment assignment was random, we should only conclude that compared to Emails, receiving a Social Media treatment is associated with a 0.0174 percentage point decrease in the probability that you'll buy a product* (confidence interval: -2.3284 to 2.2936 percentage points). Additionally, the confidence interval includes zero, so there's *not enough evidence* of a difference. 

### Limitations and Adjustments
This estimate might be wrong because of the vagueness between campaign channels as they can overlap, and conversion rates also have a distribution shift due to having much more data on customers who actually purchased the product. Additionally, the effects of advertisements may have changed between the time the data was collected (~2024) and the present day. Therefore, along with the fact that we don't know if treatment assignment was random, this result may be unreliable.
